\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-16 draft.tex
proofread intro

In constructing the model, we follow Groseclose and Snyder (1996) and Banks (2000) in taking a policy proposal as given and studing the behavior of interest groups who may lobby legislators in an attempt to sway the outcome of the vote. In order to keep the model tractable, we study a three-person legislature in which two lobbyists---one for the new proposal and one against it---sequentially offer payments to the legislators.

A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameter of a given probability distribution. Thus bribing a legislator has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers. In this environment, the optimal vote-buying strategies are not immediately obvious.

@@

Perhaps more interesting, and in contrast to results in a model without uncertainty, when only one or two legislators are bribed the legislator who remains unbribed is often he who is most ideologically-aligned with the vote buyer. When the legislators are roughly unbiased on average, it is the moderate legislator who is bribed first. This corresponds well with the data that shows that more moderate legislators receive more campaign contributions.

@@

A final result we find that is appealing from an empirical point of view: in this model, it is possible to have both vote buyers paying positive bribes on the same issue. Because the results of the model accord well with these important patterns in the data, we believe this model will contribute to the understanding of the political uncertainty that surrounds statutory lawmaking.

>>>>

In constructing the model, we follow Groseclose and Snyder (1996) and Banks (2000) in taking a policy proposal as given and studying the behavior of interest groups who may lobby legislators in an attempt to sway the outcome of the vote. In order to keep the model tractable, we study a three-person legislature in which two lobbyists---one for the new proposal and one against it---sequentially offer payments to the legislators.

A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameters of a given probability distribution. Thus bribing a legislator has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers. In this environment, the optimal vote-buying strategies are not immediately obvious.

@@

Perhaps more interesting, and in contrast to results in a model without uncertainty, when only one or two legislators are bribed the legislator who remains unbribed is often the one who is most ideologically-aligned with the vote buyer. When the legislators are roughly unbiased on average, it is the moderate legislator who is bribed first. This corresponds well with the data that shows that more moderate legislators receive more campaign contributions.

@@

We find one more result that is appealing from an empirical point of view. In this model, it is possible to have both vote buyers paying positive bribes on the same issue. Because the results of the model accord well with these important patterns in the data, we believe this model will contribute to the understanding of the political uncertainty that surrounds statutory lawmaking.
